IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-11-04 ms.tex
I a few tweaks to wording throughout on the Mie scattering fits and a reference to Yang et al. 2015.

\shorttitle{IRTF BD Spectro-photometry}
\shortauthors{BD team.}

@@

\begin{abstract}
L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres. We present a high precision ground-based study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010. 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m. 2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m. We interpret the spectral variability in 2MASS J1821 as being due to clouds with sub-micron-sized particles.
\end{abstract}

@@

The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
In addition to these direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time.
In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.

The photometry brown dwarfs at the L/T transition is explained by (silicate?) clouds at a temperature of (?).

@@

\begin{table*}
\begin{center}
\begin{tabular}{cccc}
Name & Rotation Period & Spectral Type & K magnitude \\
-- & hr & -- & -- \\
\hline \hline
2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 & 11.14 \\
2MASS J0835-019 & 9 & L5 & 11.65 \\
\end{tabular}
\end{center}
\end{table*}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
\caption{Sine fit amplitude versus wavelength with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}

Figure \ref{fig:ampspec1821mie} shows the simple Mie scattering model as compared to the data for two example particle sizes of 0.1~$\mu$m and 0.2~$\mu$m.
In these cases the reduced chi-squared values are 9.6 and 2.5 respectively, when ignoring the points within the shaded telluric contamination regions.
\section{Conclusions}

>>>>

\shorttitle{IRTF BD Spectro-photometry}
\shortauthors{Schlawin et al.}

@@

\begin{abstract}
L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres. We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010. 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m. 2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m, that can be fit by Mie extinction of sub-micron dust particles.
\end{abstract}

@@

The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
In addition to these direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.

The photometry brown dwarfs at the L/T transition is explained by (silicate and sulfide?) clouds at a temperature of (?).

@@

\begin{table*}
\begin{center}
\begin{tabular}{cccc}
Name & Rotation Period & Spectral Type & K magnitude \\
-- & hr & -- & -- \\
\hline \hline
2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 - L5 & 11.14 \\
2MASS J0835-019 & 9 & L5 & 11.65 \\
\end{tabular}
\end{center}
\end{table*}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
\caption{Sine fit amplitude versus wavelength excluding the regions contaminated by telluric absorption. with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}

Figure \ref{fig:ampspec1821mie} shows the simple Mie scattering model as compared to the data for two example particle sizes of 0.1~$\mu$m and 0.2~$\mu$m.
In these cases the reduced chi-squared values are 9.6 and 2.5 respectively, when ignoring the points within the shaded telluric contamination regions.

\citet{yang2015hstRotBD} also observe wavelength-dependent variability of 2MASS J1821.

\section{Conclusions}
